---
title: "Traumatic Brain Injury"
author: Anna Henschel
date: "2020-03-24"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Submission for #TidyTuesday week 13 "Traumatic Brain Injury" `r emo::ji("brain")`

From the Tidy Tuesday [repo](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-03-24):  

"The goal of this week's #TidyTuesday is to spread awareness for just how common TBIs are - both in civilian and military populations. **One of every 60 people in the U.S. lives with a TBI related disability. Moderate and severe traumatic brain injury (TBI) can lead to a lifetime of physical, cognitive, emotional, and behavioral changes.**  

If you want to share an infographic or summary graphic from this data - please consider using the awareness hashtag: #ChangeYourMind, #braininjuryawarenessmonth, or tagging the Brain Injury Association. More details can be found at the Brain Injury Association Website.  

The data this week comes from the CDC and Veterans Brain Injury Center. Additional stats can be found at CDC.gov."  

```{r, message=FALSE, warning=FALSE}
library(hrbrthemes)
library(ggsci)
library(scales)
library(extrafont)
library(patchwork)
library(emo)
library(Amelia)
library(tidyverse)
library(emoGG)
```

#### Load the data `r emo::ji("graph")`
```{r, message=FALSE}
# Get the Data
tbi_age <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_age.csv')
tbi_year <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_year.csv')
tbi_military <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_military.csv')
```

Exploring the data a bit (missingness etc):
```{r}
glimpse(tbi_age)

mypal = pal_d3("category10")(5) # pick 5 colours from color palette
scales::show_col(mypal)


Amelia::missmap(tbi_age, 
                col = c("#D62728FF", "#1F77B4FF"), 
                main = "Missingness Map of tbi_age")
Amelia::missmap(tbi_military, 
                col = c("#D62728FF", "#1F77B4FF"), 
                main = "Missingness Map of tbi_age")
Amelia::missmap(tbi_year, 
                col = c("#D62728FF", "#1F77B4FF"), 
                main = "Missingness Map of tbi_age")
```


#### Explore {emoGG} package `r emo::ji("smile")`
```{r}
# How does {emoGG} work?
emoji_search("tulip")

# Plot with geom_emoji
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_emoji(emoji="1f337") 

# Search codes for brain
# emoji_search("brain")
# emoji_search("bandage")
# emoji_search("bulb")
# emoji_search("baby")
# emoji_search("woman")
# emoji_search("old")
```

Relevant emojis: `emo::ji("hospital")` = `r emo::ji("hospital")`, `emo::ji("ambulance")` = `r emo::ji("ambulance")`, `emo::ji("doctor")` = `r emo::ji("doctor")`  

How to use {emoGG}:   
https://blog.revolutionanalytics.com/2015/11/emojis-in-ggplot-graphics.html 


#### Plot the TBI data `r emo::ji("metrics")`
```{r, fig.width=11, fig.height=6}
p1 <- tbi_age %>%
  filter(age_group == "0-4") %>%
  filter(type == "Emergency Department Visit") %>%
ggplot(aes(number_est, reorder(injury_mechanism, -number_est))) +
  geom_segment(aes(x = 0, y = reorder(injury_mechanism, -number_est), xend = number_est, yend = reorder(injury_mechanism, -number_est)), color = "red", size = 1) +
  geom_emoji(emoji = "1f476", size = .08) +
  scale_x_continuous(label=comma) +
  hrbrthemes::theme_ipsum_rc(grid="XY") +
  theme(axis.text.x = element_text(size =12),
        axis.text.y = element_text(size =12)) +
  labs(x = '',
       y = '',
       title = 'Traumatic Brain Injury emergency department visits (age group: 0-4)', 
       caption = 'Data by CDC • #braininjuryawarenessmonth • @AnnaHenschel')

p1
```

```{r, fig.width=11, fig.height=6}
p2 <- tbi_age %>%
  filter(age_group == "25-34") %>%
  filter(type == "Emergency Department Visit") %>%
ggplot(aes(number_est, reorder(injury_mechanism, -number_est))) +
  geom_segment(aes(x = 0, y = reorder(injury_mechanism, -number_est), xend = number_est, yend = reorder(injury_mechanism, -number_est)), color = "red", size = 1) +
  geom_emoji(emoji = "1f469", size = .08) +
  scale_x_continuous(label=comma) +
  hrbrthemes::theme_ipsum_rc(grid="XY") +
  theme(axis.text.x = element_text(size =12),
        axis.text.y = element_text(size =12)) +
  labs(x = '',
       y = '',
       title = 'Traumatic Brain Injury emergency department visits (age group: 25-34)', 
       caption = 'Data by CDC • #braininjuryawarenessmonth • @AnnaHenschel')
p2
```

```{r, fig.width=11, fig.height=6}
p3 <- tbi_age %>%
  filter(age_group == "75+") %>%
  filter(type == "Emergency Department Visit") %>%
ggplot(aes(number_est, reorder(injury_mechanism, -number_est))) +
   geom_segment(aes(x = 0, y = reorder(injury_mechanism, -number_est), xend = number_est, yend = reorder(injury_mechanism, -number_est)), color = "red", size = 1) +
  geom_emoji(emoji = "1f475", size = .08) +
  scale_x_continuous(label=comma) +
  hrbrthemes::theme_ipsum_rc(grid="XY") +
  theme(axis.text.x = element_text(size =12),
        axis.text.y = element_text(size =12)) +
  labs(x = '',
       y = '',
       title = 'Traumatic Brain Injury emergency department visits (age group: 75+)', 
       caption = 'Data by CDC • #braininjuryawarenessmonth • @AnnaHenschel')
p3
```


`r emo::ji("bulb")`Remember to tag: @biaamerica when sharing infographic!  