---
title: "FiveThirtyEight Bechdel Data"
author: Anna Henschel
output: 
  github_document:
    fig_width: 12
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bechdel data

Inspired by the following vignette by Chester Ismay: https://fivethirtyeight-r.netlify.com/articles/bechdel.html.  

Load libraries
```{r, message=FALSE, warning=FALSE}
# Bechdel data from fivethirtyeight 
library(fivethirtyeight)
# color palettes with a lot of flexibility
library(ggsci)
# pretty ggplot themes
library(ggthemes)
# more pretty ggplot themes
library(hrbrthemes)
# get more fonts
library(extrafont)
# aggregate frequencies of factors
library(janitor)
# variety of methods for reshaping data prior to analysis
library(reshape2)
 # tidy data wrangling
library(tidyverse)
# Turn off scientific notation
options(scipen = 99)
```

Load data
```{r}
# get data included in the fivethirtyeight package
data(bechdel) 

# peak at data
glimpse(bechdel)
```

How many movies pass and fail overall vs. over time?
```{r}
# Find out the overall percentage
overall_perc_bechdel <- bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  tabyl(binary)

perc_decade_bechdel <- bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  tabyl(binary, decade_code) %>%
  reshape::melt(id="binary") %>%
  rename(Decade = variable, 
         Count = value) %>%
  group_by(Decade) %>%
  mutate(Percentage = Count/sum(Count))


# See how this develops over years:
perc_bechdel_time <- bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  tabyl(year, binary) %>%
  reshape::melt(id="year")
```

A small majority of movies fails the bechdel test:
```{r}
overall_perc_bechdel %>%
  ggplot(aes(x = binary, y = percent, fill = binary)) + 
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels=scales::percent, limits = c(0,.7), breaks = c(0, .1, .2, .3, .4, .5, .6)) +
  coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_d3() +
  theme(legend.position = "none", 
        axis.text.x = element_text(size =14), 
        axis.text.y = element_text(size =14)) +
  labs(x = '', y = '',
         title = 'Proportion of movies between 1990 and 2013 passing the Bechdel Test', 
       subtitle = 'The test asks whether a work features at least two women who talk to each other about something other than a man.',
         caption = 'Data by FiveThirtyEight\n #BechdelTest • @AnnaHenschel') 
```

What does it look like by decade?
```{r}
decade_names <- c(
                    `1` = "2010 - 2013",
                    `2` = "2000 - 2009",
                    `3` = "1990 - 1999")

perc_decade_bechdel %>%
  ggplot(aes(x = binary, y = Percentage, fill = binary)) + 
  geom_bar(stat = "identity") + 
  scale_y_continuous(labels=scales::percent, limits = c(0,.7)) +
  coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_d3() +
  facet_wrap(~ Decade, 
             labeller = as_labeller(decade_names)) +
  theme(legend.position = "none", 
        axis.text.x = element_text(size =14), 
        axis.text.y = element_text(size =14)) +
  labs(x = '', y = '',
         title = 'Proportion of movies between 1990 and 2013 passing the Bechdel Test', 
       subtitle = 'The test asks whether a work features at least two women who talk to each other about something other than a man.',
         caption = 'Data by FiveThirtyEight\n #BechdelTest • @AnnaHenschel') 
```
It's a bit too early to tell with this data, as the last 7 years of the current decade are missing. But 2000 - 2009 is definitely an improvement to 1990 -1999.

```{r}
# Find out what the top international grossing movie is in each of the Bechdel Test categories
bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  filter(clean_test == "ok") %>%
  select(title, binary, clean_test, intgross) %>%
  arrange(desc(intgross))

# Find a way to do this withot manually changing the filter!
```

How does this split up in different categories?
```{r}
bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  ggplot(aes(x = clean_test, fill = clean_test)) + 
  geom_bar() + 
  ylim(0,850) +
  annotate("text", x = "nowomen", y = 220, label = "For example:\n The Hobbit:\n An Unexpected Journey", alpha = .65) +
    annotate("text", x = "notalk", y = 580, label = "For example:\n Harry Potter and\n the Deathly Hallows:\n Part 2", alpha = .65) +
    annotate("text", x = "men", y = 250, label = "For example:\n Avatar", alpha = .65) +
    annotate("text", x = "dubious", y = 200, label = "For example:\n Iron Man 3", alpha = .65) +
    annotate("text", x = "ok", y = 830, label = "For example:\n Titanic", alpha = .65) +
  theme_fivethirtyeight() +
  scale_fill_d3() +
  scale_x_discrete(labels=c("nowomen" = "Less than\n 2 women", "notalk" = "At least 2 women,\n who don't talk\n to each other","men" = "At least 2 women,\n talking about men", "dubious" = "Dubious", "ok" ="At least 2 women\n who are talking to each other\n about something else\n than men")) +
  theme(legend.position = "none", 
        axis.text.x = element_text(size =14), 
        axis.text.y = element_text(size =14)) +
  labs(x = '', y = '',
         title = 'Movies between 1990 and 2013 by Bechdel Test category', 
       subtitle = 'The test asks whether a work features at least two women who talk to each other about something other than a man.\nFor each category, an example of the highest international grossing movie is given.',
         caption = 'Data by FiveThirtyEight\n #BechdelTest • @AnnaHenschel') 
```


Does this change over time?
```{r}
ggplot(perc_bechdel_time,
       aes(x = year, y = value, colour = variable)) +
       geom_line(size = 3) +
  theme_fivethirtyeight() +
  scale_colour_d3() +
  theme(legend.position = "none", 
        axis.text.x = element_text(size =16), 
        axis.text.y = element_text(size =16)) +
  labs(x = '', y = '',
         title = 'Movies passing and failing the Bechdel test over time', 
       subtitle = 'The test asks whether a work features at least two women who talk to each other about something other than a man.',
         caption = 'Data by FiveThirtyEight\n #BechdelTest • @AnnaHenschel') 
```

Does domestic and international gross correlate?
```{r}
bechdel$decade_code <- factor(bechdel$decade_code, labels=c("2010 - 2013", "2000 - 2009", "1990 - 1999"))

import_roboto_condensed()

bechdel %>%
  filter(between(year, 1990, 2013)) %>%
  ggplot(aes(x = domgross, y = intgross, colour = as_factor(decade_code))) + 
  geom_jitter(alpha = .7, size = 4) +
  scale_x_continuous(labels = scales::dollar_format(prefix="$")) +
  scale_y_continuous(labels = scales::dollar_format(prefix="$")) +
  hrbrthemes::theme_modern_rc() +
  scale_color_startrek() +
  theme(axis.text.x = element_text(size =16), 
        axis.text.y = element_text(size =16)) +
  labs(x = '', y = '',
       colour = "By decade:", 
         title = 'Domestic and international gross of movies between 1990 and 2013',
       caption = 'Data by FiveThirtyEight\n #BechdelTest • @AnnaHenschel') 
```

Domestic gross and international gross for each movie seems highly correlated in each decade. 

